\documentclass[twocolumn]{article}

\usepackage{cite}
\usepackage[title]{appendix}

\begin{document}
% \title{MSc Project Proposal: Your Project Title}
\title{COMM424DA Project Proposal: Structural health monitoring of Offshore Wind Turbines using Functional Accelerometer Data}
\author{Jay Howarth \\
        University of Exeter \\
        MSc Data Science \\
        Supervisor: Dr Jawad Fayaz}
\maketitle

\begin{abstract}
A brief summary of the research proposal, including the research question, objectives, methodology, and significance.
\end{abstract}

\section{Introduction}
\subsection{Background}
Offshore wind turbines (OWTs) represent a critical component in the transition towards sustainable energy sources, 
offering substantial benefits due to their high energy yield and reduced visual and noise impacts compared to onshore wind farms. 
OWTs operate in harsh marine environments, subjecting them to various stressors such as strong winds, waves, and corrosive saltwater. 
These conditions can lead to structural fatigue, component degradation, and unexpected failures, posing significant safety risks and 
increasing maintenance costs.

Traditional inspection and maintenance methods for OWTs are labour-intensive, costly, and often require downtime, which affects the 
turbines' operational efficiency. There is a critical need for an effective Structural Health Monitoring (SHM) system that can continuously 
monitor the structural integrity of OWTs, detect early signs of damage, and provide timely diagnostics to prevent catastrophic failures.

\subsection{Problem Statement}
Clearly state the problem or research question you intend to address.

\section{Research Context}
Outline the main objectives of the project.

\section{Aims \& Objectives}
Review of relevant literature, identifying gaps and key theories/models.

\section{Data \& Resources}
Clearly state the research questions or hypotheses.

\section{Methodology}
FFF
\section{Research Design}
Describe the overall research design.

\section{Data Governance \& Ethics}
Explain the methods for data collection.

\section{Project Plan}
Outline the techniques for data analysis.

\section{Risk Assessment}
Specify any materials, equipment, or tools required.

\section{Conclusion}
Provide a timeline or schedule for the project\cite{gutierrez2024}.


\bibliographystyle{plain}
\bibliography{references}

\begin{appendices}
\section{Project Plan}
Stuff
\section{Code}
Stuff

\end{appendices}

\end{document}
